Country-Level Impact of Education on Entrepreneurship

### 2014-12-12 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
bib works

---
title: "Country-Level Impact of Education on Entrepreneurship"
author: "Sam Dundon and Thierry Racaud"
date: "10 December 2014"
linestretch: 2 
output: pdf_document
---

@@

**The regulatory framework**: Including administrative burdens, regulations and frameworks, as well as fiscal policy parameters.

**The market conditions**: Including anti-trust laws, rules for competition, access to foreign markets, the degree of public involvement and level of private demand.

**The access to finance**: Including access to debt financing, access to venture capital, and stock markets.

**The creation and diffusion of knowledge**: Including research and development activity, the transfer of non-commercial knowledge, co-operation among firms, technology availability, and take-up.

**The entrepreneurial capabilities**: Including business and entrepreneurship education as well as immigration.

**The entrepreneurship culture** of a population.

>>>>

---
title: "Country-Level Impact of Education on Entrepreneurship"
author: "Sam Dundon and Thierry Racaud"
date: "10 December 2014"
linestretch: 2 
output: pdf_document
bibliography: Main.bib
---

@@

- **The regulatory framework**: Including administrative burdens, regulations and frameworks, as well as fiscal policy parameters.

- **The market conditions**: Including anti-trust laws, rules for competition, access to foreign markets, the degree of public involvement and level of private demand.

- **The access to finance**: Including access to debt financing, access to venture capital, and stock markets.

- **The creation and diffusion of knowledge**: Including research and development activity, the transfer of non-commercial knowledge, co-operation among firms, technology availability, and take-up.

- **The entrepreneurial capabilities**: Including business and entrepreneurship education as well as immigration.

- **The entrepreneurship culture** of a population.
